Contention Management for 5G

### 2017-02-09 article/article.tex
harmonisation avec les nouvelles définitions en cours

\section{Introduction}
  \itemize
    \item Context and problematic
    \item Related works
    \item Article contribution

@@

@@

      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$.

@@

      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$. The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $L$. We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.

      Thus, the whole proccess time for a vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
      $$

@@

      \noindent {\bf Problem Periodic Assignment for Low Latency(PALL)}

      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.

      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?

@@

 In this section we assume that the size of a message $\tau$ is equal to one, which implies hardness of PRA and PALL for all $\tau$. 
Consider an instance of Problem PRA, i.e., a digraph $G=(V,A)$, an assignment $\cal C$, a routing function $\cal R$ and a period $P$. 
The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}_{\cal C}$.
The {\bf load} of an assignment is the maximal number of routes sharing the same arc.
It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.

@@

 Remark that we have used zero weigth in the proof. If the weigths must be strictly positive, which makes more sense in our model since
 we model the latency of physical links, it is easy to adapt the proof. We just have to set them so that in any route the delay at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$. We now lift this hardness result to the problem PALL.

@@

>>>>

\section{Introduction}
  \begin{itemize}
    \item Context and problematic
    \item Related works
    \item Article contribution
  \end{itemize}

@@

  \todo{Remplacer Dl par dl}

@@

      A {\bf route} $r$ in $G$ is a sequence of consecutive arcs $a_0, \ldots , a_{k-1}$, with $a_i=(u_i,u_{i+1}) \in A$. 
      We will often refer to the first element of the route as a source and the last as a target.

@@

      A {\bf $(P,\tau)$-periodic affectation} of a routage graph $\cal R$ is a sequence  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the number of routes in $\cal R$. The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}$ at its source.
      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}$, that is $\forall (r_i, r_j) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, in very restricted settings.
      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R}$ given in the previous subsection. 
      For each pair of routes $r_i$ and $r_j$, $v$ the first vertex which belongs to both routes,
      we set $\lambda(v,r_i) - \lambda(v,r_j)$ to $P$ instead of $1$. We chose $P$ to be an odd number smaller than $c$ the number of routes in ${\cal R}$. If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $T$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $T$. We are given a period $P$, a message size $\tau$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $(P,\tau)$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.

%       \begin{center}
%       \includegraphics[scale=0.2]{rrh.jpeg}
%       \end{center}
%       
%       This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
%       
%        \begin{center}
%       \includegraphics[scale=0.2]{BBU1.jpeg}
%       
%       \includegraphics[scale=0.2]{BBU2.jpeg}
%       \end{center}
%

      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.

      Thus, the whole proccess time for a message sent at vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
      $$

@@

      \noindent {\bf Periodic Assignment for Low Latency(PALL)}

      \noindent {\bf Input:}  a matching $\rho$ from $L$ to $S$ two disjoint set of elements, a routage graph $\cal R$ whose set of sources is $S$ and whose set of targets is $T$, a period $P$, an integer $\tau$, an integer $T_{max}$.

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation ${\cal M}$ of ${\cal R}$ such that $MT({\cal M}) \leq T_{max}$?

@@

 In this section we assume that the size of a message $\tau$ is equal to one. 
 We will prove the hardness of PRA and PALL for this parameter, which implies the hardness of the general problems. 
Consider an instance of the problem PRA, i.e., a routing graph $\cal{R}$, a message size $\tau$ and a period $P$. 
The {\bf conflict depth} of a route is the number of other routes which share an edge with it. 
The conflict depth of an assignment $\cal C$ is the maximum of the conflict depth of the routes in ${\cal R}$.
The {\bf load} of a routing graph is the maximal number of routes sharing the same arc.
It is clear that a $P$-periodic affectation must satisfy that $P$ is larger or equal to the load.

@@

 Remark that we have used zero weigth in the proof. If we ask the weigths to be strictly positive, which makes sense in our model since
they represent the latency of physical links, it is easy to adapt the proof. We just have to set them so that in any route the delay at $u_1$ is equal to $d$ and thus equal to $0$ modulo $d$. We now lift this hardness result to the problem PALL.

@@

Open questions. Can we improve the results if:
\begin{itemize}
 \item The routes are smaller than the size of a message. 
\item The routes are smaller than the period.
\item The largest difference between two routes is smallest than one of these parameters
\end{itemize}

 On a general graph:

\begin{itemize}
\item The routing is coherent
 \item The graph is symmetric
\end{itemize}
